Traffic Analysis On 6LoWPAN

### 2017-04-03 Writing/pktlen.tex
Update

\section{Packet Length}
\textit{
\begin{itemize}
	\item TLS Attacks still works and even better against DTLS due to protocol feature.
\end{itemize}
}

\subsection{ICMP Leakage}
%Plaintext recovery.
%\begin{itemize}
%	\item The attack combines packet length with MAC address information.
%	\item Works on 802.15.4 Security. No need for DTLS (ICMP is plaintext when DTLS.)
%\end{itemize}

@@

>>>>

\section{Packet Length}
Packet length is proven to be a major leakage source in Internet traffic analysis attacks. Since neither 802.15.4 Security nor DTLS protects packet length, we expect the same attacks would apply to 6LoWPAN traffic as well. Further more, we suppose 6LoWPAN applications are even more vulnerable to the leakage as there tends to be less noise in the traffic.

Unreliable transmission is more preferable for 6LoWPAN applications for its low cost. Take UDP, the symbolic protocol for unreliable transmission, for example. UDP has no flow control; therefore packet size as well as number of packets are deterministic given the same application data. This effectively removed the natural noise induced by TCP packet reassembling. Although packet fragmentation is also provided by IPv6 but this feature is usually disabled for practical reasons.

``Random" data, such as ads, is another major noise in Internet traffic which does not exist in 6LoWPAN traffic. The random data naturally randomises the traffic and hence complicates traffic analysis attacks. The leakage would be more easily observed without these noise.
\subsection{ICMP Leakage}
%Plaintext recovery.
%\begin{itemize}
%	\item The attack combines packet length with MAC address information.
%	\item Works on 802.15.4 Security. No need for DTLS (ICMP is plaintext when DTLS.)
%\end{itemize}

@@

\subsection{Countermeasure}
{\it
Pad to MTU is recommended as it completely hides the length of plaintext. This method only induces slight overhead as 6LoWPAN MTU is small and requires only negligible computation.

Unifying the drivers by strictly apply the standard MTU. Applications should be compatible to the standard anyway. 
}

### 2017-04-03 Writing/rsptime.tex
Update

\section{Response Time}
\begin{itemize}
	\item TLS attacks still works and even better against DTLS for no RTT noise. 
\end{itemize}

@@

\subsection{Different Hardware}
Gain hardware information.
\begin{itemize}
	\item Different hardware has different response latency against the same message.
	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
\end{itemize}

>>>>

\section{Response Time}
Response time is another major feature exploited in Internet traffic analysis attack. Again we would expect the same attacks can be applied to 6LoWPAN traffic and works even better than their counterparts against Internet traffic, as the accuracy of timing measurements can be greatly improved for 6LoWPAN traffic.

Firstly, the devices are physically close to each other and uses RF to communicate. The adversary can remove the RTT noises by measure the packets on the server side.

Secondly, performance of the constrained devices are low; hence gives a better resolution on timing code execution.

@@

\subsection{Different Hardware}
%Gain hardware information.
%\begin{itemize}
%	\item Different hardware has different response latency against the same message.
%	\item For 802.15.4: Requires additional information. Can be satisfied by the previous ICMP attack.
%	\item For DTLS: No requirement. The adversary can actively send a message, e.g. PING.
%\end{itemize}
